### 2016-08-10 main.tex
Change repository locations, some wording.

{\em If accepted, before final submission, all code will be moved to the Gardner Lab github repository, final release versions generated, and DOIs created as described in https://guides.github.com/activities/citable-code/ so that our results may be reproduced and the software deployed.  For now, in lieu of final release DOIs, we provide these links to our development repositories.  If you would like final versions and test datasets for review, please contact the corresponding author (bwpearre@bu.edu).}
%\marginpar{PLOS doesn't really say where such things should go.}
%\marginpar{Cleanup: mostly done.  But it would be nice to move all this to the lab's GitHub group.}
\begin{description}
  \item[Song alignment:] Jeff Markowitz's song alignment software \cite{Poole2012} can be found at
    {\tt https://github.com/jmarkow/zftftb}
\end{description}

\noindent Our implementation of the syllable
detector is available under an open-source license {\em (we are still evaluating which open source license is the most suitable for this software):}
\begin{description}
\item[Training the neural network:]\hfill
  \begin{trivlist}
  \item {\tt https://github.com/bwpearre/birds/align}
  \end{trivlist}

  \begin{description}
  \item[Installation:]\hfill
    \begin{trivlist}
    \item Clone the Github repository onto your computer.
    \end{trivlist}
  \item[Usage:]\hfill
    \begin{itemize}
      \item The main programme is {\tt learn\_detector.m}.
    \item The top section of {\tt learn\_detector.m} contains global configuration variables.  The important ones are the data directory and the bird name: as supplied, the software looks for {\tt \textless data directory\textgreater/\textless bird name\textgreater/song.mat}.  Modify as necessary.
    \item The format for the data file {\tt \textless data directory\textgreater/\textless bird name\textgreater/song.mat} is specified in {\tt birds/align/README.md}: a MATLAB file containing aligned song, nonsong (calls, cage noise, etc), and the sampling frequency.
    \item The configuration file {\tt \textless data directory\textgreater/\textless bird name\textgreater/params.m} is also described in {\tt README.md}.  If the file is empty, the programme will display an image showing the average of the song spectrograms (frequency vs.~time), tell the user how to define syllables of interest, and exit.  If {\tt times\_of\_interest} is defined, the programme will train the neural network.  {\tt params.m} can also override any of the configuration parameters at the top of {\tt learn\_detector.m}.
    \item The software will produce a neural network file, {\tt detector\_bird\_times\_\dots.mat} (the ellipses signify other information encoded in the filename).  It will also produce the audio test file described in Methods.
    \end{itemize}
  \end{description}

\item[Runtime:]\hfill
  \begin{description}
  \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
    \marginpar{Jeff: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
    \item[Usage:]\hfill
    \end{description}
  \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Download the most recent release from the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item Either connect the microphone directly into the microphone jack or through a 
      preamp into the audio input jack. If the input jack supports multiple channels (e.g., 
      audio input jacks are usually stereo), you can connect multiple audio sources and run 
      different detectors on each channel simultaneously.
      \item To generate TTL signals via the audio output, use the headphone jack. The 
      audio output must have at least the same number of channels as the input.
      \item To generate TTL signals via an Arduino, load the MATLAB arduino IO sketch 
      onto the Arduino (the sketch is available in the Github repository, and provides a 
      simple serial protocol for controlling pins). Connect the Arduino 
      to the computer via USB. The TTL signal for the first input will be available on 
      pin 7, the second input on pin 8, etc.
      \end{itemize}
    \item[Usage:]\hfill
      \begin{itemize}
      \item Use {\tt convert\_to\_text.m} to convert the Matlab output file to a format 
      easily readable by Swift. This will generate a text version of the neural network.
      \item Launch the application downloaded above. It will provide an 
      menu to select an audio input and either an audio output or an Arduino output (if 
      detected). Once you select an input and an output, a new window will show all audio 
      channels associated with the input. For each channel, select a the text-encoded version of 
      the detector created in the previous step. Once configured, press run to begin 
      monitoring the inputs.
      \end{itemize}
    \item[Customization:]\hfill
      \begin{itemize}
      \item You can clone the Github repository and use Xcode to edit the project, if you 
      are interested in extending or modifying the functionality. To hook into either 
      the raw input or output, look at the ``ViewControllerProcessor.swift'' file. The 
      {\tt Processor} class acts as a coordinator, receiving income audio, passing that
      to the detector and generating appropriate output TTL signals.
      \end{itemize}
    \end{description}
  \item[LabVIEW:] {\tt https://github.com/bwpearre/birds/align}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item The microphone should be connected through a preamplifier to the data acquisition card, by default on Analog Input 0 (AI0).
      \item Outputs are on the Digital I/O (DIO) channels.  See the block diagram of {\tt nnfft.vi} for documentation, or just connect to DIO0.
      \end{itemize}
    \item[Usage:]\hfill
      Use LabVIEW to open {\tt nnfft.vi}.  A file
      chooser is provided in the front panel.  Use it to point to the network file
      produced by {\tt learn\_detector.m}, and use LabView's ``Run''
      button to begin detection.
    \end{description}
  \end{description}

>>>>

{\em If accepted, before final submission, DOIs for the latest code will be created as described in https://guides.github.com/activities/citable-code/ so that our results may be reproduced and the software deployed.  For now, in lieu of final release DOIs, we provide these links to our development repositories.  If you would like final versions and test datasets for review, please contact the corresponding author (bwpearre@bu.edu).}
%\marginpar{PLOS doesn't really say where such things should go.}
%\marginpar{Cleanup: mostly done.  But it would be nice to move all this to the lab's GitHub group.}
\begin{description}
  \item[Song alignment:] Jeff Markowitz's song alignment software \cite{Poole2012} can be found at
    {\tt https://github.com/jmarkow/zftftb}
\end{description}

\noindent Our implementation of the syllable
detector is available under an open-source license {\em (Tentatively GPL, but we are still evaluating which open source license is the most suitable for this software):}
\begin{description}
\item[Training the neural network:]\hfill
  \begin{trivlist}
  \item {\tt https://github.com/gardner-lab/syllable-detector-learn}
  \end{trivlist}

  \begin{description}
  \item[Installation:]\hfill
    \begin{itemize}
    \item Clone the Github repository onto your computer.
    \item You also need the following packages from MATLAB File Exchange:
      \begin{description}
      \item[Significant Figures] by Teck Por Lam.  File ID \#10669.
      \item[Generate maximally perceptually-distinct colors] by Tim Holy.  File ID \#29702.
      \end{description}
    \end{itemize}
  \item[Usage:]\hfill
    \begin{itemize}
      \item The main programme is {\tt learn\_detector.m}.
    \item The top section of {\tt learn\_detector.m} contains global
      configuration variables.  The important ones are the data
      directory and the bird name: as supplied, the software looks for
      {\tt \textless data directory\textgreater/\textless bird
        name\textgreater/song.mat}.  Modify as necessary.
    \item The format for the data file {\tt \textless data
      directory\textgreater/\textless bird name\textgreater/song.mat}
      is specified in {\tt syllable-detector-learn/README.md}: a
      MATLAB file containing aligned song, nonsong (calls, cage noise,
      etc), and the sampling frequency.
    \item The configuration file {\tt \textless data
      directory\textgreater/\textless bird name\textgreater/params.m}
      is also described in {\tt README.md}.  If the file is empty, the
      programme will display an image showing the average of the song
      spectrograms (frequency vs.~time), tell the user how to define
      syllables of interest, and exit.  If {\tt times\_of\_interest}
      is defined, the programme will train the neural network.
      Optionally, {\tt params.m} can also override any of the
      configuration parameters at the top of {\tt learn\_detector.m}.
    \item The software will produce a neural network file, {\tt
      detector\_bird\_times\_\dots.mat} (the ellipses signify other
      information encoded in the filename).  It will also produce the
      audio test file described in Methods.
    \end{itemize}
  \end{description}

\item[Runtime:]\hfill
  \begin{description}
  \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
    \marginpar{Jeff: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
    \item[Usage:]\hfill
    \end{description}
  \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Download the most recent release from the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item Either connect the microphone directly into the microphone jack or through a 
      preamp into the audio input jack. If the input jack supports multiple channels (e.g., 
      audio input jacks are usually stereo), you can connect multiple audio sources and run 
      different detectors on each channel simultaneously.
      \item To generate TTL signals via the audio output, use the headphone jack. The 
      audio output must have at least the same number of channels as the input.
      \item To generate TTL signals via an Arduino, load the MATLAB arduino IO sketch 
      onto the Arduino (the sketch is available in the Github repository, and provides a 
      simple serial protocol for controlling pins). Connect the Arduino 
      to the computer via USB. The TTL signal for the first input will be available on 
      pin 7, the second input on pin 8, etc.
      \end{itemize}
    \item[Usage:]\hfill
      \begin{itemize}
      \item Use {\tt convert\_to\_text.m} to convert the Matlab output file to a format 
      easily readable by Swift. This will generate a text version of the neural network.
      \item Launch the application downloaded above. It will provide an 
      menu to select an audio input and either an audio output or an Arduino output (if 
      detected). Once you select an input and an output, a new window will show all audio 
      channels associated with the input. For each channel, select a the text-encoded version of 
      the detector created in the previous step. Once configured, press run to begin 
      monitoring the inputs.
      \end{itemize}
    \item[Customisation:]\hfill
      \begin{itemize}
      \item You can clone the Github repository and use Xcode to edit the project, if you 
      are interested in extending or modifying the functionality. To hook into either 
      the raw input or output, look at the ``ViewControllerProcessor.swift'' file. The 
      {\tt Processor} class acts as a coordinator, receiving income audio, passing that
      to the detector and generating appropriate output TTL signals.
      \end{itemize}
    \end{description}
  \item[LabVIEW:] {\tt https://github.com/gardner-lab/\dots\ syllable-detector-runtime-labview}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item The microphone should be connected, optionally through a preamplifier, to the data acquisition card, by default on Analog Input 0 (AI0).
      \item Outputs are on the Digital I/O (DIO) channels.  See the block diagram of {\tt nnfft.vi} for documentation, or just connect to DIO0.
      \end{itemize}
    \item[Usage:]\hfill
      Use LabVIEW to open {\tt nnfft.vi}.  A file
      chooser is provided in the front panel.  Use it to point to the network file
      produced by {\tt learn\_detector.m}, and use LabView's ``Run''
      button to begin detection.
    \end{description}
  \end{description}
